---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
setwd('/Users/emilyziyixiao/DataspellProjects/AdvDsFinance/HW4')
```

Type any R code in the chunk, for example:
```{r}
# Load data from csv file
df <- read.csv("autism.csv")

# Define Age and Grp variables
df$Age <- df$age - 2
df$Grp <- factor(df$sicdegp, levels=c(1,2,3), ordered=TRUE)

# Define model formulas
model_a_formula <- "vsae ~ Age + I(Age^2) + Grp + Age:Grp + I(Age^2):Grp + (0 + Age + I(Age^2) | childid)"
model_b_formula <- "vsae ~ Age + I(Age^2) + Grp + Age:Grp + I(Age^2):Grp + (0 + Age | childid)"
model_c_formula <- "vsae ~ Age + I(Age^2) + Grp + Age:Grp + (0 + Age + I(Age^2) | childid)"

# Fit models using mixed_model
library(lme4)
model_a <- lmer(formula=model_a_formula, data=df, REML=TRUE)
model_b <- lmer(formula=model_b_formula, data=df, REML=TRUE)
model_c <- lmer(formula=model_c_formula, data=df, REML=TRUE)

# Report log-likelihood for each model
cat("Model A log-likelihood:", logLik(model_a), "\n")
cat("Model B log-likelihood:", logLik(model_b), "\n")
cat("Model C log-likelihood:", logLik(model_c), "\n")

# Perform model selection
models <- list(A=model_a, B=model_b, C=model_c)
aic_values <- sapply(models, AIC)
best_model <- names(aic_values)[which.min(aic_values)]
cat("Best model according to AIC:", best_model, "\n")

```
```{r}
summary(model_a)
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
